Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
a

Esitysjärjestys: Sivun 19 slide ("Development of use of different languages in Finnish NationalBibliography") pitäisi tulla sivun 21 sliden ("Different languages in Fennica and Kungliga (percentage)") jälkeen (samalla sivun 20 slide "Development of use of different languages in Kungliga data" putoaa pois). Mutta nyt kun muutan järjestystä niin sivun 21 slide ei sen jälkeen toimi. Tämä pitää fiksata.

Karttakuvassa Greifswald, Lund ei näy. Tätä pitää vähän miettiä.

@@

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="160px"}
v <- seq(1500, 1800, 50)
selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) 
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = as.data.frame(spread(df2, publication_decade, n, fill = 0))
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {
  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal) +
     scale_x_continuous(breaks = v, labels = v)     
  print(p)

@@

### Development of use of different languages in Kungliga data

```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
catalogue = "Kungliga"
  df <- dfl %>% filter(catalog == catalogue) %>%
     	        group_by(publication_decade, language) %>%
                summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

  if (catalogue == "Fennica") {
    df <- df.full # full time span
  } else if (catalogue == "Kungliga") {
    df <- df.full # full time span
  }
  df <- df %>% filter(catalog == catalogue)%>%
        filter(publication_year >= 1600 & publication_year <= 1900)

@@

### Printing of theology in different languages in Turku

```{r topics-101, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel =  c("kirkkohistoria","raamatunhistoria","eksegetiikka","homiletiikka","dogmatiikka","teologia")
catalogue <- "Fennica"

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= 1640 & publication_year <= 1800)
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}
# Selected catalogue with selected topics
df <- dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
  print(p)
```

>>>>

Karttakuvassa Greifswald, Lund ei näy. Tätä olisi hyvä saada kehitettyä, tällaisena tää ei ihan toimi.

@@

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="170px"}
v <- seq(1500, 1800, 50)
selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) 
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = as.data.frame(spread(df2, publication_decade, n, fill = 0))
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {
  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal) +
     scale_x_continuous(breaks = v, labels = v)     
  print(p)

@@

@@

  if (catalogue == "Fennica") {
    df <- df.full # full time span
  } else if (catalogue == "Kungliga") {
    df <- df.full # full time span
  }
  langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
  df <- df %>% filter(catalog == catalogue)%>%
        filter(publication_year >= 1600 & publication_year <= 1900)

@@
